The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-02 article.tex
Systematic benchmarking framework and preliminary results.
cdkversion everywhere

\title{The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching}

@@

Due to limited developer resources we envision that releases will primarily 
increment the minor version with the occasional patch release. As per Maven 
convention, development versions are suffixed with \texttt{-SNAPSHOT}. 
There are no API changes from v1.5.x and v2.0.

@@

>>>>

\title{The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching}

@@

Due to limited developer resources we envision that releases will primarily 
increment the minor version with the occasional patch release. As per Maven 
convention, development versions are suffixed with \texttt{-SNAPSHOT}. 
There are no API changes from v1.5.x and \cdkversion{}.

@@

\subsection*{Table ? }
\begin{tabular}{llllllll}
Benchmark  & Data Set & Input Format & \multicolumn{2}{c}{CDK 1.4.19} & \multicolumn{2}{c}{CDK \cdkversion{}} & Improvement \\
           &          &              & Skipped & Elapsed Time         & Skipped  & Elapsed Time \\
\hline
\multirow{4}{*}{countheavy} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 37.14s  & 9    & 3.32s & x11.18 \\
                            &                            & 
    SDfile & 0              & 15.97s  & 25   & 10.45s & x1.52 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 14.75s \\
                            &                              & 
    SDfile &                &         & 0    & 1m12.08s \\
\hline
\multirow{4}{*}{rings --mark} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 37.53s  & 9    & 4.42s & x8.49 \\
                            &                            & 
    SDfile & 0              & 18.64s  & 25   & 12.26s & x1.52 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 34.48s \\
                            &                              & 
    SDfile &                &         & 0    & 1m24.59s \\
\hline
\multirow{4}{*}{rings --sssr} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 48.83s  & 9    & 5.17s & x9.44 \\
                            &                            & 
    SDfile & 0              & 28.24s  & 25   & 12.54s & x2.25 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 32.91s \\
                            &                              & 
    SDfile &                &         & 0    & 1m28.02s \\
\hline
\multirow{4}{*}{rings --all} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2126           & 1m5.74s  & 26    & 12.96s & x5.07 \\
                            &                            & 
    SDfile & 16             & 49.91s  & 40   & 4.53s & x11.01 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 30.03s \\
                            &                              & 
    SDfile &                &         & 0    & 1m28.65s \\
\hline
\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 58.43s  & 9    & 6.00s & x9.74 \\
                            &                            & 
    SDfile & 0              & 37.28s  & 26   & 13.82s & x2.69 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 46.43s \\
                            &                              & 
    SDfile &                &         & 0    & 1m48.43s \\
\hline
\multirow{4}{*}{convert -ofmt=smi} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 54.96s  & 9    & 4.85s \\
                            &                            & 
    SDfile & 35             & 47.05s  & 29   & 11.70s \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 35.42s \\
                            &                              & 
    SDfile &                &         & 0    & 1m38.08s \\
\hline
\multirow{4}{*}{convert -ofmt=sdf} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 53.61s  & 9    & 19.47s & x2.82 \\
                            &                            & 
    SDfile & 13             & 38.31s  & 29   & 35.08s & x1.09 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 5m44.59s \\
                            &                              & 
    SDfile &                &         & 0    & 7m0.96s \\
\hline
\multirow{4}{*}{convert --gen2d -ofmt=sdf} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 36m49.59s  & 9    & 1m9.82s & x31.64 \\
                            &                            & 
    SDfile & 13             & 25m39.99s  & 29   & 1m29.09s & x17.28 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 18m55.64s & \\
                            &                              & 
    SDfile &                &         & 0    & 20m55.64s \\
\hline
\multirow{4}{*}{genfp --type=maccs} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2150           & 100m1.61s  & 9    & 26.53s & x226 \\
                            &                            & 
    SDfile & ?              & ??.??s     & 25   & 35.46s \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 13m48.73s \\
                            &                              & 
    SDfile &                &         & 0    & 14m4.49s \\
\hline
\multirow{4}{*}{genfp --type=path} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2150           & ??.??s     & 9    & 3.32s \\
                            &                            & 
    SDfile & ?              & ??.??s     & 25   & 10.45s \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 50.12s \\
                            &                              & 
    SDfile &                &         & 0    & 57.71s \\
\hline
\multirow{4}{*}{genfp --type=ecfp4} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2150           & ??.??s     & 26    & 50.12s \\
                            &                            & 
    SDfile & ?              & ??.??s     & 40   & 57.71s \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES &                &         & 9    & 22m50.2s \\
                            &                              & 
    SDfile &                &         & 0    & 23m58.27s \\\hline

\end{tabular}
